---
title: "Normality Check App"
author: "Catherine Torres"
date: "10/05/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Description

This application will allow you to check the normality of four numeric variables from the *iris* data.

The application is running on: https://catherine-torres.shinyapps.io/Normality_check/

The ui.R and Server.R Code can be found in the github repository: https://github.com/cathetorres/normality-check

## The *iris* data

```{r, echo = TRUE}
summary(iris)
```

## How to use the application

First, choose which variable you want to check the normality:

- Sepal.Length
- Sepal.Width
- Pepal.Length
- Pepal.Width

## Checking the normality with plots

You can check the normality with two types of plots:

```{r}
par(mfrow = c(1,2))
hist(iris$Sepal.Width, main = "(1) Histogram")
qqnorm(iris$Sepal.Width, main = "(2) QQ plot")
```

## Checking the normality with tests

You can also check the normality by using the Shapiro-Wilks test:

```{r}
shapiro.test(iris$Sepal.Width)
```
